\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dhanush Neelakantan} \\ \vspace{1pt}
    \small 571-583-7884 $|$ \href{mailto:dhanushneelakantan2002@gmail.com}{dhanushneelakantan2002@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/dhanush-neelakantan-15b4481bb/}{linkedin.com/in/dhanush-neelakantan} $|$
    \href{https://github.com/Dhanush4448}{github.com/Dhanush4448}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {Master of Science in Computer Science; GPA: 3.7/4.0}{Expected May 2026}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: Python (Adv.), SQL (Postgres), Node.js, Next.js 16, React, FastAPI, Java, TypeScript} \\
     \textbf{Cloud/DevOps}{: GCP (GKE, Cloud SQL), Docker, Kubernetes, Jenkins CI/CD, Nginx, Artifact Registry, Linux} \\
     \textbf{Systems/Backend}{: Distributed Systems, Multiprocessing, Prisma 7, SQLAlchemy, Redis, MongoDB, HPA, JWT} \\
     \textbf{Tools/Testing}{: Chaos Engineering, Pytest, Postman, Gcloud CLI, OpenSSL, Webpack, Git Monorepos}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graduate Teaching Assistant (IT 366 - Network Security)}{Aug. 2025 -- Present}
      {George Mason University}{Fairfax, VA}
      \resumeItemListStart
        \resumeItem{Facilitated technical labs and reviews for 50+ students on network security protocols and SDLC security.}
        \resumeItem{Refactored grading automation for system configurations, increasing scoring consistency for 100+ submissions.}
        \resumeItem{Automated administrative pipelines for performance tracking, reducing manual processing time by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Developer Intern}{Oct. 2021 -- Apr. 2022}
      {digi Tran Solutions}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Built and maintained production Node.js backend used by \textbf{1,500+ active chefs}, reducing order processing latency by \textbf{25\%} via performance-tuned API routes.}
        \resumeItem{Improved API throughput under concurrent load by optimizing \textbf{Redis caching strategies} and \textbf{MongoDB indexes/schema} access patterns.}
        \resumeItem{Implemented \textbf{JWT-based RBAC} to secure service endpoints, reducing unauthorized access attempts by \textbf{65\%}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Sentinel GCP: Enterprise Security Platform} $|$ \emph{Next.js 16, TypeScript, PostgreSQL, GCP}}{2025-2026}
          \resumeItemListStart
            \resumeItem{Solved enterprise authentication and security monitoring challenges by building production-ready dashboard with \textbf{Next.js 16}, implementing \textbf{Google OAuth}, persistent database sessions, and \textbf{4-tier RBAC} (USER, ADMIN, MODERATOR, VIEWER) for secure access control and audit compliance.}
            \resumeItem{Implemented comprehensive security layer with \textbf{Content Security Policy (CSP)}, \textbf{HSTS headers}, distributed rate limiting (\textbf{Upstash Redis}/in-memory fallback), \textbf{Zod input validation}, and \textbf{CSRF protection}, ensuring \textbf{OWASP Top 10 compliance} and preventing XSS, SQL injection, and unauthorized access attacks.}
            \resumeItem{Optimized application performance through \textbf{Prisma ORM connection pooling}, \textbf{in-memory caching with TTL}, and strategic database indexing, achieving \textbf{sub-50ms database query latency} and reducing API response times through intelligent caching strategies.}
            \resumeItem{Designed and deployed production infrastructure with \textbf{Docker multi-stage builds}, \textbf{GCP Cloud Run auto-scaling} (0-10 instances), \textbf{GCP Secret Manager} integration, and \textbf{GitHub Actions CI/CD}, achieving one-command deployment with zero-downtime updates and comprehensive observability through structured logging, health checks, and metrics API.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Sentinel OTA: Resilient Parallel Recovery Engine} $|$ \emph{Python, GCP, PostgreSQL}}{2026}
          \resumeItemListStart
            \resumeItem{Architected high-throughput pipeline for \textbf{10,000+ IoT devices}, migrating data to GCP Cloud SQL with distributed recovery engine using Python's multiprocessing across 4 CPU cores.}
            \resumeItem{Achieved \textbf{100\% recovery rate} for 3,300+ failed device logs by sharding datasets and implementing idempotent operations for data consistency.}
            \resumeItem{Integrated \textbf{Chaos Engineering suite} to inject data corruption; designed non-blocking sanitization layer to quarantine "dirty data" into manual triage queue.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Cloud-Native CI/CD Survey Platform} $|$ \emph{GKE, Jenkins, Docker, Nginx}}{2025}
          \resumeItemListStart
            \resumeItem{Deployed containerized web application on \textbf{Google Kubernetes Engine (GKE)} with 3-pod high-availability config and \textbf{HPA} scaling (3-6 replicas) based on 60\% CPU utilization.}
            \resumeItem{Built \textbf{Jenkins CI/CD Pipeline} automating source cloning, Docker builds, and pushes to GCP Artifact Registry.}
            \resumeItem{Implemented \textbf{Nginx reverse proxying} for load balancing and SSL termination, improving endpoint security and performance.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Full-Stack Student Survey App} $|$ \emph{React, FastAPI, SQLModel, GCP Cloud SQL}}{2025}
          \resumeItemListStart
            \resumeItem{Developed multi-tier CRUD application using \textbf{React.js} and \textbf{FastAPI} with \textbf{SQLModel/SQLAlchemy} for asynchronous database sessions.}
            \resumeItem{Engineered relational mapping layer enabling complex query filtering for historical survey trends with sub-second response times.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
